HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-24 scnn.tex

>>>>

A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
to use the traditional 2-dimensional convolution on an irregular grid defined on the
sphere. In the paper, two grids are used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}. See \figref{sphere_grids}. Because this
approach is based on the classic 2-dimensional convolution, it benefits from all the optimizations developed for images and is very likely to be
the most computationally efficient one. However, it suffers that it can only be used using very
specific grid sampling sets which are not including HEALPix. Furthermore, the
grid requirement makes it impossible for the convolution to capture the
spherical properties of the domain, i.e., the cubed-sphere sampling is by
definition adapted to a cube and not to a sphere.
Those samplings are not ideal as their resolution is not constant across the sphere. Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled. Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence.
% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e. (i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution. Do you think we should mention that? I think we should not.}
